---
title: "Produce View"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
date: "2025-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide",
	fig.width = 9,
	fig.height = 7
)

library(aws.s3)
library(nanoparquet)
library(dplyr)
library(lubridate)
library(ggplot2)
library(forcats)
library(purrr)
library(ukfsr)

pv <- aws.s3::s3read_using(FUN = nanoparquet::read_parquet, object = "ProduceView/produce_view.parquet", bucket = "s3-ranch-045")
pv <- pv |> mutate(date = ymd(date))

```

## What this is

The data is a log of SKUs and country of origins available in a sample of
supermarkets. The profiles are a summary of counts of these SKU records. No
indication of volume of available product or sales is implied. Its assumed that
diversity of SKUs implies more product on sale, but this is not necessarily the
case. A homogeneous product may sell in great volume but only have a small
number of records in the data.


## Product profiles {.tabset .tabset-pills}

### Categories

```{r product-profile-cat}


cats <- pv |> count(category) |> pull(category)

purrr::map(cats, \(x) {
  
pv |> 
  filter(!category %in% c("Mushrooms", "Prepared")) |> 
  mutate(month = month(date),
         country = fct(country)) |>
  filter(!country %in% c("NA", "Non Shown"), !is.na(country), category == x) |> 
  mutate(country = fct_lump_n(country, n = 4)) |> 
  ggplot() +
  geom_bar(aes(x = month, fill = country), position = "fill", stat = "count") + 
  scale_y_continuous(labels = scales::label_percent()) +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  scale_fill_manual(values = afcolours::af_colours(type = "categorical")) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(), legend.title = element_blank()) +
  labs(title = x,
       x = NULL,
      y= NULL)
})

```


### Sub categories

```{r product-profile-subcat}


cats <- pv |> count(sub_category) |> pull(sub_category)

purrr::map(cats, \(x) {
  
pv |> 
  mutate(month = month(date),
         country = fct(country)) |>
  filter(!country %in% c("NA", "Non Shown"), !is.na(country), sub_category == x) |> 
  mutate(country = fct_lump_n(country, n = 4)) |> 
  ggplot() +
  geom_bar(aes(x = month, fill = country), position = "fill", stat = "count") + 
  scale_y_continuous(labels = scales::label_percent()) +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  scale_fill_manual(values = afcolours::af_colours(type = "categorical")) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(), legend.title = element_blank()) +
  labs(title = x,
       x = NULL,
      y= NULL)
})

```

### Product group

```{r product-profile-prodgrp}


cats <- pv |> count(product_group) |> pull(product_group)

purrr::map(cats, \(x) {
  
pv |> 
  mutate(month = month(date),
         country = fct(country)) |>
  filter(!country %in% c("NA", "Non Shown"), !is.na(country), product_group == x) |> 
  mutate(country = fct_lump_n(country, n = 4)) |> 
  ggplot() +
  geom_bar(aes(x = month, fill = country), position = "fill", stat = "count") + 
  scale_y_continuous(labels = scales::label_percent()) +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  scale_fill_manual(values = afcolours::af_colours(type = "categorical")) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(), legend.title = element_blank()) +
  labs(title = x,
       x = NULL,
      y= NULL)
})

```

## Country profiles {.tabset .tabset-pills}

### Sub categories

```{r country-profile-subcat}

countries <- pv |> count(country) |> pull(country)

purrr::map(countries, \(x) {

  pv |> 
  mutate(month = month(date),
         sub_category = fct(sub_category)) |>
  filter(!country %in% c("NA", "Non Shown"), !is.na(country), country == x) |> 
  mutate(sub_category = fct_lump_n(sub_category, n = 4)) |> 
  ggplot() +
  geom_bar(aes(x = month, fill = sub_category), position = "fill", stat = "count") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_x_continuous(limits = c(1, 12), breaks = 1:12, labels = month.abb) +
  scale_fill_manual(values = afcolours::af_colours(type = "categorical")) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(), legend.title = element_blank()) +
  labs(title = x,
       x = NULL,
       y= NULL)

})
  
```


### Product group
  
```{r country-profile-prodgrp}

countries <- pv |> count(country) |> pull(country)

purrr::map(countries, \(x) {

  pv |> 
  mutate(month = month(date),
         product_group = fct(product_group)) |>
  filter(!country %in% c("NA", "Non Shown"), !is.na(country), country == x) |> 
  mutate(product_group = fct_lump_n(product_group, n = 4)) |> 
  ggplot() +
  geom_bar(aes(x = month, fill = product_group), position = "fill", stat = "count") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_x_continuous(limits = c(1, 12), breaks = 1:12, labels = month.abb) +
  scale_fill_manual(values = afcolours::af_colours(type = "categorical")) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(), legend.title = element_blank()) +
  labs(title = x,
       x = NULL,
       y= NULL)

})
  
```




